---
title: Brazil data
author: Ricardo Mayer
date: '2018-01-16'
categories:
  - data
tags:
  - data
  - Brazil
slug: brazil-data
---

```{r setup, message=FALSE, echo=FALSE}
options(knitr.table.format = "html", knitr.kable.NA = '') 
library(kableExtra)
library(tidyr)
library(dplyr)
library(timetk)
library(readxl)
library(lubridate)
library(purrr)
library(forecast)
library(ggplot2)
library(tibbletime)
```


## Data sources and definition

## Data storage 

## Data exploration

### Data loading

load
```{r data_load}
country_q <- read_excel("../../Brasil.xlsx", sheet = "quarterly")
country_m <- read_excel("../../Brasil.xlsx", sheet = "monthly")
```



clean up

```{r cleanup,  message=FALSE, warning=FALSE}
data_q <- country_q %>% select(-c(year, quarter, trim, hlookup)) %>% 
  filter(!is.na(rgdp))

data_m <- country_m %>% select(-c(year, month,  hlookup)) 

data_q$date <- ymd(data_q$date)
data_m$date <- ymd(data_m$date)
```

Three versions of the data set for different purposes:
- multicolumn ts (mts) object 
- multicolumn xts object
- a tibble with list column, to apply functions for each series and store results as another list column (think estimation model, results, etc)

```{r reshape_and_nesting, message=FALSE, warning=FALSE}
start_year_q <- min(year(data_q$date))
start_year_m <- min(year(data_m$date))

data_q_mts <- tk_ts(data_q, start = start_year_q, frequency = 4)
data_q_xts <- tk_xts(data_q, date_var = date)
data_q_tbt <- as_tbl_time(data_q, index = date)
data_q_long <- data_q %>% gather(variable, value, -date)

data_q_nested <- data_q_long %>% group_by(variable) %>% 
  nest(.key = "data.tbl")
data_q_n_ts <- data_q_nested %>% 
  mutate(data.ts = map(.x   =  data.tbl,
                       .f   =  tk_ts,
                       start = start_year_q,
                       freq = 4
                       )
         )

data_m_mts <- tk_ts(data_m, start = start_year_m, frequency = 12)
data_m_xts <- tk_xts(data_m, date_var = date)
data_m_tbt <- as_tbl_time(data_m, index = date)
data_m_long <- data_m %>% gather(variable, value, -date)

data_m_nested <- data_m_long %>% group_by(variable) %>% 
  nest(.key = "data.tbl")
data_m_n_ts <- data_m_nested %>% 
  mutate(data.ts = map(.x   =  data.tbl,
                       .f   =  tk_ts,
                       start = start_year_m,
                       freq = 12
                       )
         )

```

Some plots

Quaterly variables
```{r plotq, message=FALSE, warning=FALSE}
plotbase_q <- ggplot(data = data_q_long,
                     aes(x = date, y = value, colour = variable))  

plot_q <- plotbase_q + geom_line() + 
  facet_wrap(~variable, scales = "free_y", ncol = 3) 

plot_q
```


Monthly variables
```{r plotm, message=FALSE, warning=FALSE}
plotbase_m <- ggplot(data = data_m_long,
                     aes(x = date, y = value, colour = variable))  

plot_m <- plotbase_m + geom_line() + 
  facet_wrap(~variable, scales = "free_y", ncol = 3) 

plot_m
```


## Summary of properties


